---
title: "Covid19"
author: "Julius Okanta"
date: "2024-11-01"
output: html_document
---

# This is a beginner project on R

## Understanding the data

loading the library and reading file
```{r}
library(readr)
covid_df <- read_csv(
  "C:/Users/Julius Agyei Okanta/OneDrive/Desktop/URV Health Data Science/Projects R/Guided Projects/covid-19/covid19.csv"
)
```

Checking dimension of dataframe
```{r}
dim(covid_df)
```
Checking column names of dataframe
```{r}
vector_cols <- colnames(covid_df)
```
Displaying first 10 rows
```{r}
head(covid_df, 10)
```
Viewing columns
```{r}
View(covid_df)
```
summary of covid_df
```{r}
library(tibble)
glimpse(covid_df)
summary(covid_df)
```

## Isolating the data needed

In the dataset, Province_State column has data of different levels - country level and state/province level.To compare results among countries, there is the need to filter data for "All_states" for the analysis. 

- Selecting data for `"All States"` and removing `Province State`

```{r}
library(dplyr)

covid_df_all_states <- covid_df %>%
  filter(Province_State == "All States") %>%
  select(-Province_State)
```